```latex
\section{Credibility Inference}

The credibility graph defines how sources and claims are connected, but does not, on its own, provide any information about the credibility of either. Next, we describe an iterative inference algorithm that computes the credibility of each source, based on the properties of the network.

In this way, the algorithm keeps iterating between the source nodes and the claim nodes. Sources distribute their credibility among the claims they assert, and then these claims redistribute their accumulated support back to the sources that assert them. Repeating this process causes the source credibility vector to converge toward a stable distribution.

\subsection{Propagation Algorithm}

Propagation consists of four stages that are done at each iteration step. In the first one, source credibility is propagated to the claims they assert. After this stage, in the second one, support for claims is aggregated from all asserting sources. After the aggregation process, the result is propagated back to the source nodes. Finally, the credibility vector is normalized before the next iteration begins. The following subsections describe each stage formally.

\subsection{Claim Support}

For the first stage in each iteration, the support for each claim is computed. In doing so, each of the sources distributes their credibility evenly across all of the claims that it asserts. Hence, sources that assert a lot of claims will have less credibility per claim as compared to the sources that assert fewer claims.

Claim $c_j$ receives support according to the formula:

\[
c_j =
\sum_{i \in A(j)}
\frac{s_i}{d_i}.
\]

Here, $s_i$ is the credibility of source $i$, $d_i$ is the number of claims from source $i$, and $A(j)$ is the set of sources asserting claim $j$.

\subsection{Source Update}

The second step of the iteration process is updating the credibility of each source. This is done using the support from each claim that the source asserts. Because claims can be asserted by multiple sources, the support for each claim is divided evenly across all of the sources asserting it. Therefore, a source with highly supported claims will have high credibility.

The new credibility of source $s_i$ is calculated according to the formula:

\begin{equation}
s_i' =
\sum_{j \in C(i)}
\frac{c_j}{a_j}.
\end{equation}

Here, $c_j$ is the support of claim $j$, $a_j$ is the number of sources asserting claim $j$ and $C(i)$ is the set of claims asserted by source $i$.

\subsection{Normalization}

The obtained credibility vector must be normalized after each step before moving on to the next step to maintain proportionality of the sources' credibility without changing its norm in future iterations.

We normalize the credibility of source $s_i$ according to the following formula:

\begin{equation}
s_i =
\frac{s_i'}
{\sum_k s_k'}.
\end{equation}

where $s_i'$ is the updated credibility of source $i$ before normalization.

\subsection{Convergence}

The propagation process continues repeatedly until the source credibility vector converges to a stable distribution. In each step, the obtained source credibility vector is compared with the source credibility vector from the previous step. The convergence process is completed when the maximal difference between corresponding credibility values falls below a predefined threshold.

Convergence criterion:

\begin{equation}
\max_i
\left|
s_i^{(t+1)}
-
s_i^{(t)}
\right|
<
\varepsilon,
\end{equation}

where $s_i^{(t)}$ is the credibility of source $i$ after iteration $t$, and $\varepsilon$ is the threshold value of convergence.